Plant Metagenomic Barcoding of Pollen Loads Offers Insights on the Foraging

### 2022-11-28 script/manuscript_MEE.Rmd
too tired

Kraken2 was able to identify the species richness of pollen samples ($\bar{x}$ = , min = , max = ). Bracken was able to estimate the relative abundance of pollen grains in each sample (max % of any species, $\bar{x}$ % of all species, min % trace amounts detected). BLAST, the most thorough sequence alignment algorithm,

@@

## 3.5 | Floral Observations ?

@@

>>>>

Kraken2 was able to identify the species richness of pollen samples ($\bar{x}$ = , min = , max = ). Bracken was able to estimate the relative abundance of pollen grains in each sample (max % of any species, $\bar{x}$ % of all species, min % trace amounts detected). BLAST, the most thorough sequence alignment algorithm...

@@

## 3.5 | Floral Observations

@@

```{r Most used resources by species, echo = F}

corb <- read.csv('../data/Corbiculae_collections.csv', header = F) %>% 
  mutate(sample.id = as.numeric(str_extract(V1, '[0-9]{1,2}')),
         species = str_extract(V1, 'Bombus [^ ]+'),
         caste = str_trim(str_extract(V1, '[:space:][q|w][:space:]'))) %>% 
  filter(caste == 'q') %>% 
  select(-V1, -caste)

blst <- read.csv('../data/classified_blast.csv') %>% 
  distinct(sample.id)

blst <- read.csv('../data/classified_blast.csv') %>% 
  mutate(across(where(is.character), ~ replace_na(., 'UNKNOWN'))) %>% 
  arrange(sample.id, -Prcnt_seqs) %>% 
  inner_join(., corb, by = 'sample.id')

blst_cnt <- blst %>% 
  distinct(sample.id, .keep_all = T) %>% 
  count(species)

tb <- blst %>% 
  left_join(., blst_cnt, by = 'species') %>% 
  group_by(species, name) %>% 
  mutate(Mu_Seqs = sum(Prcnt_seqs)/n)  %>% 
  distinct(species, name, .keep_all = T)

tb %>% 
  filter(species == 'Bombus appositus') %>% 
  ungroup() %>% 
  mutate(total = sum(Mu_Seqs))

obs <- read.csv('../data/yearEndInteractionsObservations.csv')[,2:5] %>% 
  group_by(species) %>% 
  arrange(species, -bySpp) %>% 
  slice_head(n = 10)
